%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Research Experience}

\begin{cventries}

    %------------------------------------------------

    \cventry
    {Research Assistant (part-time)} % Job title
    {National Cybersecurity R\&D Lab, NUS} % Organization
    {Singapore} % Location
    {Jan. 2021 - PRESENT} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Working on research projects related to the secure application of Intel SGX.
        \end{cvitems}
    }

    %------------------------------------------------

    \cventry
    {Final Year Projcet} % Job title
    {School of Cyber Science and Engineering, SJTU} % Organization
    {Shanghai, China} % Location
    {Jan. 2020 - May. 2020} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Built a system for secure multi-party computation by integrating Intel SGX and EOS.io smart contract.
        \end{cvitems}
    }

    %------------------------------------------------

    \cventry
    {Independent Project} % Job title
    {National Cybersecurity R\&D Lab, NUS} % Organization
    {Singapore} % Location
    {Aug. 2019 - Dec. 2019} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Proposed a solution to reduce attestation overhead caused by frequent communication in a multi-node network on Intel SGX.
            \item Ported a \textit{Raft} implementation into SGX enclaves to build a consensus network between SGX enclaves.
        \end{cvitems}
    }

    %------------------------------------------------

    \cventry
    {Trainee} % Job title
    {Lab of Cryptography and Computer Security, SJTU} % Organization
    {Shanghai, China} % Location
    {Sept. 2018 - Jan. 2020} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Presented fundamental points on \textit{Key Agreement Schemes}, \textit{Secret Sharing Schemes}, \textit{Network Access Control} and \textit{Bitcoin Wallets}.
            \item Implemented digest algorithm \textit{SM3} and embeded it into \textit{OpenSSL} (not published).
            \item Built a proof-of-concept project to improve consensus efficiency using two-layer Honey Badger BFT.
        \end{cvitems}
    }

    %------------------------------------------------

\end{cventries}

%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\newpage

\cvsection{Project Experience}

\begin{cventries}

    %------------------------------------------------

    \cventry
    {Developer} % Job title
    {Network \& Information Center, SJTU} % Organization
    {Shanghai, China} % Location
    {Aug. 2020 - Feb. 2021} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Built a web service to request and deliver electronic official transcripts with digital signature for undergraduate students.
            \item The system has been put into use in February 2021 and served 1.8k students and delivered nearly 3k transcripts till now.
        \end{cvitems}
    }

    %------------------------------------------------

    % \cventry
    % {Contestant} % Job title
    % {School of Cyber Science and Engineering, SJTU} % Organization
    % {Shanghai, China} % Location
    % {Mar. 2019 - Jul. 2019} % Date(s)
    % { % Description(s) of tasks/responsibilities
    %     \begin{cvitems}
    %         \item National College Student Information Security Contest
    %         \item Developed a blockchain-based online shopping platform oriented to protect user privacy.
    %     \end{cvitems}
    % }

    %------------------------------------------------

    \cventry
    {33rd Participation in Research Program (T401PRP33005)} % Job title
    {Network \& Information Center, SJTU} % Organization
    {Shanghai, China} % Location
    {Jun. 2017 - Oct. 2018} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Worked on the project \textit{Optimized Design and Implementation of the Website for the Management of Network Information}
            \item Developed a website for thousands of students to self-service hostel network affairs and for staff to deal with enquires.
            \item Led development of the front-end part using Vue.js and built most of the webpages public to users.
        \end{cvitems}
    }

    %------------------------------------------------

\end{cventries}
