%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Research on Blockchain} % Job title
{Loccs (Lab of Cryptography and Computer Security, SJTU)} % Organization
{} % Location
{Sept. 2018 - PRESENT} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Attended training on Cryptography Theory and Practice, Network Security Essentials and Bitcoin.}
\item {Presented fundamental points on Key Agreement Schemes, Secret Sharing Schemes, Network Access Control and Bitcoin Wallets.}
\item {Implemented digest algorithm SM3 and embeded it into OpenSSL (not published).}
\item {Currently preparing for presentation on EOS.io, scratching to learn about Byzantine Fault Tolerance.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Contestant} % Job title
{National College Student Information Security Contest} % Organization
{} % Location
{Feb. 2018 - PRESENT} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Currently working on the development of a privacy-friendly online shoping platform, which is designed to leverage blockchain.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Core Member} % Job title
{33rd Participation in Research Program (T401PRP33005)} % Organization
{} % Location
{June. 2017 - Oct. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked on Optimized Design and Implementation of the Website for the Management of Network Information (NIMO).}
\item {Particapted actively in front-end part of the project using Vue.js. I started up the front-end project, searched and applyed all required frameworks and librarys and optimized the infrastructure.In addition to this, most of the pages exposed to public was written by me.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}