%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{State of Purpose}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\lettersection{Academic Interest}

I have a great interest in blockchain technology and implementation of security protocols on IoT platforms.

Blockchain is a technology that leverages cryptography theory and distributed storage technology, which makes it decentralized. These features ensure that the data on it cannot be tampered and less likely to lose, hence it may do well in documenting the facts. At the same time, user privacy may be well protected with the help of asymmetric cryptosystem.

Many things are still to be done to promote the application of blockchain technology. We need reasonable mechanisms to claim ownership or inherit others property on blockchain without increasing the risk of leaking user privacy. Without such mechanisms, people would doubt cryptocurrencies' safety and the government would also deny the legitimacy of them for it's hard to tax on. Approaches shall be proposed to link blockchain together with realistic world in specific applications as well. Although data on blockchains can't be tampered, we have few means to verify the authenticity of what was uploaded, which makes it difficult to check the integrity of data on the chain. Only if we could make sure that the input of blockchain is valid, can people trust data on the blockchain and apply it in real world,

I believe that there will be some new situations which couldn't be better without blockchains in the future, though there seem to be few things that we can do better using blockchain technology at present. While blockchain was built on cryptography and distributed consensus algorithms, the improvement of blockchain would also benefit the development of cryptography engineering and distributed computing technology.

Apart from blockchain, implementing cryptographic algorithms and security protocols are also fantastic jobs. Efficient and secure implementation of cryptographic algorithms and security protocols is the cornerstone of modern network technology. In the application of IoT, where privacy matters a lot, safe and efficient implementation is more important. So, I'm willing to dedicate to improve the security of IoT equipment by implementing these algorithms.

In LoCCS, the lab I currently work in, I have learned some basic knowledge about cryptography theory, network essentials and basic concepts of Bitcoin. We are still being trained on other topics about mainstream cryptocurrencies and blockchain technologies, such as Ethereum, Zillqa, EOS.io. And I complete a project independently to integrate digest method SM3 to a modified version of OpenSSL. These are far from enough, and I'm always on the way to learn more and do more.

%------------------------------------------------

\lettersection{Future Planning}

For my study in NUS, if there is a chance, I'd like to complete 3 modules of coursework as well as Independent Project (CP3106).

Considering my bachelor's degree, I am required to complete 3 elective modules at NUS to meet the requirements of graduation qualification review. Cryptography Theory and Practice (CS4236) is the best substitution for Modern Cryptography; Advanced Operating Systems (CS5250) is meant to substitute for Development practice for system software; and Computer Security (CS3235) might be a substitution for Network Security Defense Technology.

These well-designed courses in NUS will benefit me a lot. Advanced Operating Systems let me know more about operating systems, which is a wonderful supplement for my undergraduate lesson Operating System. As an old says goes, review the past and you'll know better the present. In spite LoCCS has taught me something about Cryptography Theory and Practice, learning it again from a different perspective will give me new inspiration. Finally, Computer Security will provide a broad understanding of security topics, which could be interesting and practical.

It might be a little difficult to achieve an excellent result with a 5-4-3 configure as well as CP3106, but I have the confidence to take the challenges and do my best.

%------------------------------------------------

\end{cvletter}