%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Research Experience}

\begin{cventries}

    %------------------------------------------------

    \cventry
    {Research Assistant (Part-time, Supervised by Assoc. Prof. Chang Ee-Chien)} % Job title
    {National Cybersecurity R\&D Lab, NUS} % Organization
    {Singapore} % Location
    {Jan. 2021 - PRESENT} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Working on research projects related to the secure application of Intel SGX.
            \item We have submitted a research paper, where I conducted all of the experiments.
        \end{cvitems}
    }

    %------------------------------------------------

    \cventry
    {Course Project for Programming Language Implementation (Supervised by Assoc. Prof. Martin Henz)} % Job title
    {School of Computing, NUS} % Organization
    {Singapore} % Location
    {Jan. 2021 - Apr. 2021} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Implemented a middleware for the \href{https://source-academy.github.io/source/SOUNDS/index.html}{SOUNDS} Library in Source Academy.
            \item The middleware partially evaluates the sounds that students programmed into a function computed parallelly by GPU.js.
            \item Our project managed to half the time required to process the sounds.
        \end{cvitems}
    }

    %------------------------------------------------

    \cventry
    {Final Year Projcet (Supervised by Assoc. Prof. Fan Lei)} % Job title
    {School of Cyber Science and Engineering, SJTU} % Organization
    {Shanghai, China} % Location
    {Jan. 2020 - May. 2020} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Designed a system for secure multi-party computation by integrating Intel SGX and EOS.io smart contract.
            \item The system is designed to provide security assurance with regards to confidentiality and integrity and to be rollback-resistant.
        \end{cvitems}
    }

    %------------------------------------------------

    \cventry
    {Independent Project (Supervised by Assoc. Prof. Chang Ee-Chien)} % Job title
    {National Cybersecurity R\&D Lab, NUS} % Organization
    {Singapore} % Location
    {Aug. 2019 - Dec. 2019} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Proposed a solution to reduce attestation overhead caused by frequent communication in a multi-node network on Intel SGX.
            \item Ported a {Raft} implementation into SGX enclaves to build a consensus network between SGX enclaves.
            \item My proposal reduced the communication complexity from \(O\left(n^2\right)\) to \(O(n)\).
        \end{cvitems}
    }

    %------------------------------------------------

    \cventry
    {Trainee} % Job title
    {Lab of Cryptography and Computer Security, SJTU} % Organization
    {Shanghai, China} % Location
    {Sep. 2018 - Jan. 2020} % Date(s)
    { % Description(s) of tasks/responsibilities
        \begin{cvitems}
            \item Presented fundamental points on {Key Agreement Schemes}, {Secret Sharing Schemes}, {Network Access Control} and {Bitcoin Wallets}.
            \item Implemented digest algorithm {SM3} and embeded it into {OpenSSL} (not published).
            \item Built a proof-of-concept project to improve consensus efficiency using two-layer Honey Badger BFT.
        \end{cvitems}
    }

    %------------------------------------------------

\end{cventries}
