%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.1 (9/1/2016)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry

\fontdir[fonts/] % Specify the location of the included fonts


% Color for highlights
\colorlet{awesome}{awesome-orange} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
% \definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
% \definecolor{graytext}{HTML}{414141}
% \definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\input{cv-sections/00-premable.tex}

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

% \recipient{Company Recruitment Team}{Initech Inc.\\4120 Freidrich Ln.\\Austin, TX 78744} % The company being applied to

% \letterdate{\today} % The date on the letter, default is the date of compilation

% \lettertitle{Job Application for Middle Manager} % The title of the letter

% \letteropening{Dear Mr./Ms./Dr. LastName,} % How the letter is opened

% \letterclosing{Sincerely,} % How the letter is closed

% \letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

\makecvfooter{\today}{Jiamin SHEN~~~·~~~Personal Statement}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed

%----------------------------------------------------------------------------------------

\begin{document}

\newfontfamily\custombodyfont[
  Path=./fonts/,
  UprightFont=*-Regular,
  ItalicFont=*-Italic,
  BoldFont=*-Bold,
  BoldItalicFont=*-BoldItalic,
]{Merriweather}

\renewcommand{\bodyfont}{\custombodyfont}

\newfontfamily\custombodyfontlight[
  Path=./fonts/,
  UprightFont=*-Light,
  ItalicFont=*-LightItalic,
  BoldFont=*-Regular,
  BoldItalicFont=*-Italic,
]{Merriweather}

\renewcommand{\bodyfontlight}{\custombodyfontlight}

\makecvheader % Print the header

% \makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

    %------------------------------------------------

    \lettersection{About me}

    I'm an undergraduate student studying at Shanghai Jiao Tong University, majoring in Information Security.
    In the fall of 2019, I attended the Non-Graduating Non-Exchange Programme held by School of Computing, National University of Singapore.
    I would like to pursue a Master's Degree in Infocomm Security from NUS.

    %------------------------------------------------

    \lettersection{Why this programme?} % your reasons for applying to the programme

    I chose to major in Information Security for my Bachelor's Degree only because it was far more difficult to get into a programme in Computer Science.
    But only after my learning more about security, did I find it interesting and meaningful to work on security and research security problems.
    With the development of information technology, people are more and more dependent on computers and network.
    Thus there must be someone dedicate into protecting the network application and infrastructure or facilitating trusts between unknown people.

    National is one of the most excellent universities in Asia and ranks top in Computer Security and Cryptography research.
    During the NGNE Programme, I experienced a great education model and rigorous academic atmosphere.

    Therefore, I am longing for furthering my study via the Master's Programme in Infocomm Security.

    % My current research interest is on Intel Software Extension and Blockchain.

    % Blockchain is a technology that leverages cryptography theory and distributed storage technology, which makes it decentralized.
    % These features ensure that the data on it cannot be tampered and less likely to lose, hence it may do well in documenting the facts.
    % At the same time, user privacy may be well protected with the help of asymmetric cryptosystem.



    % Many things are still to be done to promote the application of blockchain technology.
    % We need reasonable mechanisms to claim ownership or inherit others property on blockchain without increasing the risk of leaking user privacy.
    % Without such mechanisms, people would doubt cryptocurrencies' safety and the government would also deny the legitimacy of them for it's hard to tax on.
    % Approaches shall be proposed to link blockchain together with realistic world in specific applications as well.
    % Although data on blockchains can't be tampered, we have few means to verify the authenticity of what was uploaded, which makes it difficult to check the integrity of data on the chain.
    % Only if we could make sure that the input of blockchain is valid, can people trust data on the blockchain and apply it in real world,

    % I believe that there will be some new situations which couldn't be better without blockchains in the future, though there seem to be few things that we can do better using blockchain technology at present.
    % While blockchain was built on cryptography and distributed consensus algorithms, the improvement of blockchain would also benefit the development of cryptography engineering and distributed computing technology.

    % Apart from blockchain, implementing cryptographic algorithms and security protocols are also fantastic jobs.
    % Efficient and secure implementation of cryptographic algorithms and security protocols is the cornerstone of modern network technology.
    % In the application of IoT, where privacy matters a lot, safe and efficient implementation is more important.
    % So, I'm willing to dedicate to improve the security of IoT equipment by implementing these algorithms.

    % Love for Security
    % 	majored in Security and found it interesting
    % 	Interested in SGX technology.

    % Want to live for several years in Singapore

    % Like NUS.
    %     Ranks top in Cryptography and Computer Security.
    %     Attended the NGNE programe of NUS Comp.
    %     The only one stays in Security topics.

    %------------------------------------------------

    \lettersection{Preparation for Infocomm Security} % your preparation for the field of study

    I've learned how to program in C++ (CS902 98) and taught myself with other programming languages such as Python and JavaScript.
    To improve efficiency, I built some tiny tools which help to download the timetable in iCalendar format, to classify PDF pages by page size, or to monitor an SMS platform for replies.
    I also participated in a web project which aims to provide an office automation system for students' network managers.
    During these projects, I improved my programming skills and learned how to build applications based on the need of users and how to work with others.

    In the field of security, I've also learned basic topics in security (IS304 97, IS497 96, NUS CS3235 A).
    And I partially got some knowledge of system security in (IS405 92) and formal perspective of cryptography in (NUS CS4236 A+).
    To attend the National College Student Information Security Contest, our group developed a blockchain-based online shopping platform oriented on protecting user privacy, which won the second prize.

    I attended \textit{\textbf{Lab of Cryptography and Computer Security}} in SJTU in September 2018, where I learned my first knowledge about cryptography theory, network essentials and basic concepts of Bitcoin and blockchain. By giving and listening to reports, I learned how to organize a presentation.
    Under the guidance of the teacher, I completed a project independently to integrate digest algorithm SM3 to a modified version of OpenSSL. This project led me to a deeper exploration of OpenSSL.
    I also helped to build a proof-of-concept project, which tried to improve consensus efficiency by sharding and two-layer consensus.

    During my internship in \textit{\textbf{National Cybersecurity R\&D Lab}} in the fall of 2019, supervised by Chang Ee-Chien, I learned what is Intel Software Extension and how to use it.
    During that semester, I proposed a method of mutual attestation between enclaves which significantly reduced the overhead on communication.
    And I successfully migrate an open-source implementation of Raft into SGX, which utilized the mutual attestation protocol in a multi-node network.

    In this semester, I'm doing my Final Year Project continuing my interest in Blockchain and SGX.
    The project requires to design a new smart contract system supporting secure multiparty computation utilizing the consistency provided by blockchain and security guarantee provided by SGX.

    I believe I can complete the programme well, both in courses and in research.

    %------------------------------------------------

    \lettersection{Career Plans} % future career plans

    After completing the master programme, I plan to accumulate some experience in the industry first.
    But finally, I'd like to come back to the university to be a teacher.
    Because I'm keen on sharing my knowledge and ideas to help students who don't know computers step into the world of programming and security.

    If possible, I will also seek opportunities to turn to a PhD program.
    %------------------------------------------------

    \lettersection{Last but not least} % other aspects of your background and interests that may help in the evaluation of your aptitude and motivation for graduate studies

    I completed my IELTS Academic test on Decemember 1st, 2019.
    But I haven't received my score report because of the epidemic.
    Thus I have no way other than upload an screenshot of the IELTS results with a reference ID on it to prove my IELTS score.

    %------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

% \makeletterclosing % Print the signature and enclosures

\end{document}